Random Forests, LAs

### 2025-01-21 presentations/web_diffusion.Rmd

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture1.png){width="70%"} -->
![](images/Picture1.png){width="70%"}

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/archive/nuts/figure/Picture2.png){width="70%"} -->
![](images/Picture2.png){width="70%"}

@@

<!-- <small> -->

<!-- -   Tranos, E., and C. Stich. 2020. Individual internet usage and the -->

<!--     availability of online content of local interest: A multilevel -->

<!--     approach. *Computers, Environment and Urban Systems*, 79:101371. -->

<!-- -   Tranos, E., T. Kitsos, and R. Ortega-Argilés. 2021. Digital economy -->

<!--     in the UK: Regional productivity effects of early adoption. -->

<!--     *Regional Studies*, 55:12, 1924-1938. -->

<!-- -   Stich, C., E. Tranos and M. Nathan. 2022. Modelling clusters from -->

<!--     the ground up: a web data approach. *Environment and Planning B*, in -->

<!--     press. -->

<!-- -   Tranos, E., A. C. Incera and G. Willis. 2022. Using the web to -->

<!--     predict regional trade flows: data extraction, modelling, and -->

<!--     validation, *Annals of the AAG*, in press. -->

<!-- </small> -->

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

```{r UK S, eval=T, out.width = "60%", out.height="60%"}
#, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"

path.image <- paste0(path, "/outputs/s_uk_per_firm.png")
knitr::include_graphics(path.image)
```

```{r LA_S_gif, eval=F, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/s_lad_per_firm/")

@@

```{r Xmid_frequency_graph, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/xmid_f.png")
knitr::include_graphics(path.image)
```

@@

```{r diffusion_speed_map, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/speed_pam.png")
knitr::include_graphics(path.image)
```

@@

<!-- fast  -->

```{r Darlington, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000005.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Nottingham, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000018.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Reading, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000038.png")
knitr::include_graphics(path.image)
```

@@

```{r City_of_London, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E09000001.png")
knitr::include_graphics(path.image)
```

@@

```{r Middlesbrough, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000002.png")
knitr::include_graphics(path.image)
```

@@

```{r Leicester, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000016.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Bristol, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000023.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Plymouth, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E06000026.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Liverpool, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E08000012.png")
knitr::include_graphics(path.image)
```

@@

```{r Hackney, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_E09000012.png")
knitr::include_graphics(path.image)
```

<!-- ------------------------------------------------------------------------ -->

```{r Edinburgh, eval=F, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_lad_per_firm/lad_S12000036.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only05.png")
knitr::include_graphics(path.image)
```

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only95.png")
knitr::include_graphics(path.image)
```

@@

<!-- ------------------------------------------------------------------------ -->

```{r, eval=FALSE, heatmaps, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

<!-- ------------------------------------------------------------------------ -->

```{r eval = F, heatmaps_log, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/")

list.files(path = path.images, pattern = "^hex_log1", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

@@

<!-- -   Website density regressions -- distance effect -->

@@

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/la_ggplot/morani_la.csv")

read.csv(path.in) %>% dplyr::select(year, morani) %>% 
  ggplot(aes(x=year, y=morani)) +
  geom_bar(stat = "identity") + 
  ylab('Moran\'s I') +
  theme_minimal() +
  ggtitle("Moran\'s I, websites per firm a Local Authority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

@@

```{r, eval=T, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/lisa/oa_ggplot/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

read.csv(path.in) %>% dplyr::select(year, morani) %>% 
  ggplot(aes(x=year, y=morani)) +
  geom_bar(stat = "identity") + 
  ylab('Moran\'s I') +
  theme_minimal() +
  ggtitle("Moran\'s I, websites per Output Area") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/la_ggplot/lisa/")

list.files(path = path.images, pattern = "^lisa_level_pc1_la", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

```{r lisa_oa, eval=T,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/oa_ggplot/lisa/")

@@

<!-- ## Website density regressions -->

<!-- $$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$ -->

<!-- ::: {style="margin-left: 50px !important; text-align:left !important"} -->

<!-- $Website\,Density_{i}$: -->

<!-- -   Websites per firm in a Local Authority $i$, *or* -->

<!-- -   Websites in an Output Area $i$ -->

<!-- ::: -->

<!-- ## Website density regressions -->

<!-- $$Website\,Density_{i} = a + \beta Distance\,to\,Place_{i} + e_{i}$$ -->

<!-- ::: {style="margin-left: 50px !important; text-align:left !important"} -->

<!-- $Place$: -->

<!-- -   London, *or* -->

<!-- -   Nearest city, *or* -->

<!-- -   Nearest retail centre -->

<!-- ::: -->

<!-- ## Website density regressions -->

<!-- $\beta$ interpretation: -->

<!-- -   The lower the $\beta$ is (or the larger the $|\beta|$ is)... -->

<!-- -   ... the larger urban gravitation is for web adoption. -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_London_la, fig.height=5, fig.width=5, message=FALSE} -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_london_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_city_la, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_city_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_centre_la,  fig.height=5, fig.width=5,message=FALSE} -->

<!-- #, out.height= "60%", out.width="60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_centre_la.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_London_oa, eval=T, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_london_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_centre_oa, eval = T,  fig.height=5, fig.width=5,message=FALSE} -->

<!-- #fig.height=4, fig.width=4,  -->

<!-- #, out.height= "60%", out.width="60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_city_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r b_city_oa, eval = T, fig.height=5, fig.width=5, message=FALSE} -->

<!-- #, out.width = "60%" -->

<!-- path.image <- paste0(path, "/outputs/lisa/b_dist_centre_oa.png") -->

<!-- knitr::include_graphics(path.image) -->

<!-- ``` -->

<!-- ------------------------------------------------------------------------ -->

<!-- ```{r r_squared, eval=T, results='asis'} -->

<!-- # This is for the RSquared of the different website density regressions. -->

<!-- path.in1 <- paste0(path, "/outputs/lisa/r2_all_oa.csv") -->

<!-- path.in2 <- paste0(path, "/outputs/lisa/r2_all_la.csv") -->

<!-- # read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>%  -->

<!-- #   ggplot(aes(x=year)) + -->

<!-- #   geom_line(aes(y=London, color = "OA to London"), size=1) + -->

<!-- #   geom_line(aes(y=cities, color = "OA to nearest city"), size=1) + -->

<!-- #   geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) + -->

<!-- #  -->

<!-- #   geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) + -->

<!-- #   geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) + -->

<!-- #   geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) + -->

<!-- #  -->

<!-- #   scale_color_discrete(name = "R-squared for regression:") + -->

<!-- #   #scale_linetype_manual(name = "Website density regressions111")  -->

<!-- #   ylab("R-squared") +  -->

<!-- #   ggtitle("Website density regressions") + -->

<!-- #   theme_minimal() + -->

<!-- #   theme(axis.title.x=element_blank(), -->

<!-- #         plot.title = element_text(hjust = 0.5)) -->

<!-- read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>%  -->

<!--   pivot_longer(!year, names_to = "regression", values_to = "Rsquared") %>%  -->

<!--   mutate(LA = if_else(str_ends(regression, ".LA"), " to LA", "to OA"), -->

<!--          regression = str_remove_all(regression, ".LA"), -->

<!--          line = paste0(regression, " ", LA)) %>%  -->

<!--   ggplot() + -->

<!--   geom_line(aes(x=year, y = Rsquared, color = line), -->

<!--             size = 1) + -->

<!--   scale_color_discrete(name = "R-squared for regression:") + -->

<!--   #scale_linetype_manual(name = "Website density regressions111")  -->

<!--   ylab("R-squared") +  -->

<!--   ggtitle("Website density regressions") + -->

<!--   theme_minimal() + -->

<!--   theme(axis.title.x=element_blank(), -->

<!--         plot.title = element_text(hjust = 0.5)) -->

<!-- #   scale_color_manual(values = c("red", "blue", "green")) -->

<!-- ``` -->

@@

```{r gini_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/gini_la.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, websites per firm in Local Auhtority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

```{r gini_oa, eval=T, results='asis'}
path.in <- paste0(path, "/outputs/lisa/gini_oa.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, websites per Output Area") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

@@

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.032 | 0.810    | 0.019 |
| Output Areas        | 5.000 | 0.205    | 1.047 |

@@

## Variable importance for Local Authorities

```{r varimpLA, eval = T, out.height= "58%", out.width="58%", message=FALSE}

path.image <- paste0(path, "/outputs/rf/figures/varimp_LA.png")
knitr::include_graphics(path.image)
```

## Variable importance for Output Areas

```{r varimpOA, eval = T, out.height= "58%", out.width="58%", message=FALSE}
#,  fig.height=5, fig.width=5,message=FALSE

path.image <- paste0(path, "/outputs/rf/figures/varimp_OA.png")
knitr::include_graphics(path.image)
```

@@

```{r similarity, eval = T, message=FALSE}
path.lad <- paste0(path, "/outputs/rf/figures/test_regions_LA.csv")
path.oa <- paste0(path, "/outputs/rf/figures/test_regions_OA.csv")

@@

## Alternative specification: growth, trained on all data

<br> <small>
$$Website\,Density\,Growth_{t} \sim \color{orange}{Distance\,London} + 
\color{orange}{Website\,density\,London_{t-1}} + \\
\color{orange}{Distance\,Nearest\,City} + 
\color{orange}{Website\,density\,Nearest\,City_{t-1}} + \\
\color{orange}{Distance\,Nearest\,Retail_{i}} +
\color{orange}{Website\,density\,Nearest\,Retail_{t-1}} +\\
\color{olive}{W*\, Website\,density_{t-1}} +\\ 
\color{violet}{year_{t}}$$ </small>

|                     | RMSE  | RSquared | MAE   |
|---------------------|-------|----------|-------|
| Local Authorities\* | 0.200 | 0.634    | 0.148 |

## Alternative specification: growth, trained on all data

```{r growth LA}
path.table <- paste0(path, "/outputs/rf/figures/test_regions_LA_growth.csv")
read.csv(path.table) %>% 
  mutate(Rsquared = round(Rsquared, digits= 3)) %>% 
  arrange(desc(Rsquared)) %>% 
  kable()
```

>>>>

![](images/Picture1.png){width="70%"}

@@

![](images/Picture2.png){width="70%"}

@@

@@

![](images/screenshot_directory_website_2010.png)

@@

![](images/screenshot_2010.png)

@@

```{r UK S, eval=T, out.width = "60%", out.height="60%"}

path.image <- paste0(path, "/outputs/s/s_uk_per_firm.png")
knitr::include_graphics(path.image)
```

```{r LA_S_gif, eval=F, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/s/s_lad_per_firm/")

@@

```{r Xmid_frequency_graph, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/xmid_f.png")
knitr::include_graphics(path.image)
```

@@

```{r diffusion_speed_map, fig.height=5, fig.width=5, message=FALSE, out.width = "100%"}
path.image <- paste0(path, "/outputs/s/speed_map.png")
knitr::include_graphics(path.image)
```

@@

```{r Reading, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/s_lad_per_firm/lad_E06000038.png")
knitr::include_graphics(path.image)
```

@@

```{r City_of_London, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/s_lad_per_firm/lad_E09000001.png")
knitr::include_graphics(path.image)
```

@@

```{r Middlesbrough, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/s_lad_per_firm/lad_E06000002.png")
knitr::include_graphics(path.image)
```

@@

```{r Bristol, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/s_lad_per_firm/lad_E06000023.png")
knitr::include_graphics(path.image)
```

@@

```{r Hackney, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s/s_lad_per_firm/lad_E09000012.png")
knitr::include_graphics(path.image)
```

@@

```{r , eval=T, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/ranks/web_per_firm2000_2012_only0595_av.png")
knitr::include_graphics(path.image)
```

@@

@@

@@

```{r moransi, results='asis'}
path.in.la <- paste0(path, "/outputs/lisa/corrected/LA/morani_la.csv")
path.in.oa <- paste0(path, "/outputs/lisa/corrected/oa/morani_oa.csv")

la.m <- read_csv(path.in.la) %>% 
  filter(p < 0.001) %>% # all values were significant
  mutate(spatial.unit = 'LAD')
oa.m <- read_csv(path.in.oa) %>% 
  filter(p < 0.001) %>% # all values were significant
  mutate(spatial.unit = 'OA')

bind_rows(la.m, oa.m) %>% 
  ggplot(aes(x=year, y=morani, fill= spatial.unit)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  ylab('Moran\'s I') +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual('Spatial unit', 
                    values = c("LAD" = "grey80",
                                "OA"="grey48"),
                     limits = force) +
  scale_x_continuous(NULL, labels = as.character(1996:2012), breaks = 1996:2012) +
  theme(legend.position="bottom",
        text = element_text(size = 12),
        legend.text=element_text(size=12),
        legend.title=element_text(size=12),
        axis.title=element_text(size=12),
        axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
```

@@

```{r lisa_la, results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/corrected/la/")

list.files(path = path.images, pattern = "^lisa_level_pc1_la", full.names = T)[-c(1,2)] %>%
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(delay=50) #%>% # animates, can opt for number of loops
  #image_write("test.gif") # write to current dir
```

@@

```{r lisa_oa, eval=T,results='asis', out.width = "60%"}
path.images <- paste0(path, "/outputs/lisa/corrected/oa/")

@@

@@

```{r gini, results='asis'}
path.in.la <- paste0(path, "/outputs/gini/gini_la.csv")
path.in.oa <- paste0(path, "/outputs/gini/gini_oa.csv")

la.gini <- read_csv(path.in.la) %>% 
  mutate(spatial.unit = 'LAD')
oa.gini <- read_csv(path.in.oa) %>% 
  mutate(spatial.unit = 'OA')

bind_rows(la.gini, oa.gini) %>%
  rename(Gini = 'gini(a$n)') %>% 
  ggplot(aes(x=year, y=Gini, fill= spatial.unit)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  ylab('Gini') +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual('Spatial unit', 
                    values = c("LAD" = "grey80",
                                "OA"="grey48"),
                     limits = force) +
  scale_x_continuous(NULL, labels = as.character(1996:2012), breaks = 1996:2012) +
  theme(legend.position="bottom",
        text = element_text(size = 12),
        legend.text=element_text(size=12),
        legend.title=element_text(size=12),
        axis.title=element_text(size=12),
        axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=1))
```

@@

|                    | RMSE  | $R^{2}$   | MAE   |
|--------------------|-------|-----------|-------|
| Local Authorities\*| 0.028 | 0.850     | 0.019 |
| Output Areas       | 3.284 | 0.320     | 1.034 |

@@

## Variable importance

```{r varimp, eval = T, out.height= "58%", out.width="58%", message=FALSE}
path.importance.lad <- paste0(path, "/outputs/rf/figures/varimp_LA_corrected.csv")
path.importance.oa <- paste0(path, "/outputs/rf/figures/varimp_OA_corrected.csv")

importance.oa <- read_csv(path.importance.oa) %>% 
  mutate(id = c("LD", "NC", "NR", "STL", "Y", "DL", "DNC", "DNR")) %>% 
  mutate(variable = str_to_sentence(variable))
importance.lad <- read_csv(path.importance.lad) %>% 
  mutate(id = c("LD", "NC", "STL", "Y", "DL", "DNC")) %>% 
  mutate(variable = str_to_sentence(variable))

importance.oa %>% 
  rename(OA = importance) %>% 
  left_join(importance.lad %>% rename(LAD = importance), by = "id") %>%
  dplyr::select(-variable.y, -id) %>% 
  rename(variable = variable.x) %>% 
  pivot_longer(!variable, names_to = "spatial.unit", values_to = "importance") %>% 
  mutate(order = ifelse(variable == "Distance to london", 1,
                        ifelse(variable == "London's wensite density, t-1", 2,
                               ifelse(variable == "Distance to the nearest city", 3,
                                      ifelse(variable == "Nearest city's wensite density, t-1", 4,
                                             ifelse(variable == "Distance to the nearest retail centre", 5,
                                                    ifelse(variable == "Nearest retail centre's wensite density, t-1", 6,
                                                           ifelse(variable == "Spatial and temporal lag of wensite density", 7, 8)))))))) %>% 
  ggplot(aes(x=importance, y=reorder(variable, desc(order)), #forcats::fct_reorder(variable, importance), 
         fill = spatial.unit)) +
  geom_col(position = 'dodge') +
  ylab('') +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(vjust = 0.5, hjust=1)) +
  scale_fill_manual('Spatial unit: ', 
                    values = c("LAD" = "grey80",
                                "OA"="grey48"),
                     limits = force) +
  scale_x_continuous('Variable importance') +
  theme(legend.position="bottom",
        text = element_text(size = 14),
        legend.text=element_text(size=14),
        legend.title=element_text(size=14),
        axis.title=element_text(size=14))
```

@@

```{r similarity, eval = T, message=FALSE}
path.lad <- paste0(path, "/outputs/rf/figures/test_regions_LA_corrected.csv")
path.oa <- paste0(path, "/outputs/rf/figures/test_regions_OA_corrected.csv")

@@

<!-- ## Alternative specification: growth, trained on all data -->

<!-- <br> <small> -->
<!-- $$Website\,Density\,Growth_{t} \sim \color{orange}{Distance\,London} +  -->
<!-- \color{orange}{Website\,density\,London_{t-1}} + \\ -->
<!-- \color{orange}{Distance\,Nearest\,City} +  -->
<!-- \color{orange}{Website\,density\,Nearest\,City_{t-1}} + \\ -->
<!-- \color{orange}{Distance\,Nearest\,Retail_{i}} + -->
<!-- \color{orange}{Website\,density\,Nearest\,Retail_{t-1}} +\\ -->
<!-- \color{olive}{W*\, Website\,density_{t-1}} +\\  -->
<!-- \color{violet}{year_{t}}$$ </small> -->

<!-- |                     | RMSE  | RSquared | MAE   | -->
<!-- |---------------------|-------|----------|-------| -->
<!-- | Local Authorities\* | 0.200 | 0.634    | 0.148 | -->

<!-- <small> \*No retail centre predictors for the Local Authority models -->
<!-- </small> -->

<!-- ## Alternative specification: growth, trained on all data -->

<!-- ```{r growth LA} -->
<!-- path.table <- paste0(path, "/outputs/rf/figures/test_regions_LA_growth.csv") -->
<!-- read.csv(path.table) %>%  -->
<!--   mutate(Rsquared = round(Rsquared, digits= 3)) %>%  -->
<!--   arrange(desc(Rsquared)) %>%  -->
<!--   kable() -->
<!-- ``` -->

### 2025-01-21 src/la_RF_corrected_10.Rmd

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df,# %>% filter(year > 1999),                   # FILTER BY YEAR FOR GROWTH
                                spacevar = "ladcd",
                                timevar = "year", 
                                k = 10)

>>>>

```{r}
set.seed(123)
indices <- CreateSpacetimeFolds(df,# %>% filter(year > 1999),                   # FILTER BY YEAR FOR GROWTH
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = 10)
